An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-25 article.tex
Fixed counting error. Added T-test summaries.

The first subset of data was used for Model 1 and Model 2 (see Table 1). This subset contained 5298 samples spanning the period from 2012 to 2022, covering 57 GI Regions and 1432 separate vineyards.

@@

% This table is absolutely trash.
% Kate madea good point that, although figures can be combined into a single figure. Tables cannot.
% cheat way to multi line comment
\iffalse{}
  \caption{Ftests and wsutff}\label{tab:ftests}
    \begin{tabular}{@{}cllllllll@{}}
       & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope 1\\ Emissions\end{tabular}}} & \textbf{Year} & \textbf{\begin{tabular}[c]{@{}l@{}}GI\\ Region\end{tabular}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ *\\ Scope 1\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ *\\ Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Year\\ *\\ GI\\ Region\end{tabular}}} \\ \midrule
      \textbf{Model 1} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 3211 & 10.4 & 6.6 & 70.6 & 1507.1 &  &  &  \\
      F-Value & 34187.908 & 110.255 & 70.56 & 83.533 & 297.163 &  &  &  \\
      Pr(>F) & 2.20E-16 & 2.20E-16 & 2.20E-16 & 2.20E-16 & 2.20E-16 &  &  &  \\
      \multicolumn{1}{l}{} &  &  &  &  &  &  &  &  \\
      \textbf{Model 2} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 2856.23 & 473.32 & 33.06 &  &  & 53.47 & 0.28 & 975.61 \\
      F-Value & 15363.1866 & 177.8109 & 2545.9357 &  &  & 287.6126 & 1.5097 & 12.3766 \\
      Pr(>F) & <2e-16 & <2e-16 & <2e-16 &  &  & <2e-16 & 0.2192 & <2e-16 \\
      \multicolumn{1}{l}{} &  &  &  &  &  &  &  &  \\
      \textbf{Model 3} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 2142.46 & 0.32 & 0.04 & 13.24 & 649.83 &  &  &  \\
      F-Value & 84905.8197 & 12.5874 & 1.4915 & 87.4771 & 515.0601 &  &  &  \\
      Pr(>F) & <2.2E-016 & 0.0003947 & 0.2220844 & <2.2E-016 & <2.2E-016 &  &  &  \\
      \multicolumn{1}{l}{} &  &  &  &  &  &  &  &  \\
      \textbf{Model 4} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 1868.46 & 274.92 & 0.04 &  &  & 35.02 & 4.18 & 582.96 \\
      F-Value & 44084.0278 & 6486.2867 & 0.8311 &  &  & 826.1925 & 98.5895 & 56.6019 \\
      Pr(>F) & <2e-16 & <2e-16 & 0.3621 &  &  & <2e-16 & <2e-16 & <2e-16
\fi
% model 1 - all sig
% model 2 - area * water used interaction was not sig
% model 3 - scope 1 was not sig
% model 4 - scope 1 was not sig
To determine if predictors significantly related to a Model's response variable, F-tests were conducted. Aside from 3 variables, all F-tests across each model indicated a significant contribution at 95\% confidence (See Table
%\ref{tab:ftests}).
). The exceptions were scope 1 emissions in models 3 and 4, as well as the interaction between area harvested and water used in Model 3. 
Models 1 and 2 showed significant linear relationships present between all predictors and their response variables (with P-values being less than 2.200E-16). Predictors in Models 3 and 4 reported the same significance for each variable except for scope 1 emissions. Scope 1 emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients scope 1 emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yield and average price per tonne as a ratio to area harvested, respectively).

@@

T-tests were used to determine if predictors significantly contributed to their models when accounting for other variables; this allowed a more granular examination of interactions and factors within categorical variables, showing which specific years and areas contributed significantly and which did not (see appendix).
% The range of how significant these variable were is important.
% How many were important vs how many were not?
% was it the same across each of the models? For example was one year/region always bad for every model?
With regard to continuous variables, Model 1 and 2 showed water use, scope 1 emissions and area harvested were significant when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope 1 emissions were significant. Model 4 showed scope 1 emissions and water use to only be significant when considered as an interaction with area harvested but not when considered on their own.
\subsubsection{Model Coefficients}
% A map and a table just like the t-test section.
\begin{figure}
\caption{Violine plot of GI Region and Year coefficients for each model.}\label{fig:violin}
\includegraphics{violinplot.pdf}
\end{figure}

>>>>

The first subset of data was used for Model 1 and Model 2 (see Table 1). This subset contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 separate vineyards.

@@

To determine if predictors significantly related to a Model's response variable, F-tests were conducted. Aside from 3 variables, all F-tests across each model indicated a significant contribution at 95\% confidence. The three exceptions were: scope 1 emissions in Model 3 (P=2.221E-01) and Model 4 (P=3.621E-01), and Model 2's interaction between area harvested and water used (P=2.192E-01).
Scope 1 emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients scope 1 emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yield and average price per tonne as a ratio to area harvested, respectively).

@@

T-tests were used to determine if predictors significantly contributed to their models when accounting for other variables; this allowed a more granular examination of interactions and factors within categorical variables, showing which specific years and areas contributed significantly and which did not (the appendix contains a comprehensive list of these values).

For Models 1 and 3, depicting yield and value as totals, year played a pivitol role; with only one year in each model not being significant (2021/2022 and 2016/2017 respectively). Both Model 1 and 3 showed a majority of regions were significant with 32 of 54 regions being significant in Model 1 and 42 of 50 regions being significant in Model 3.

For Model 1, All years were significant except for the 2021/2022 financial year (where, P=4.325E-01). 32/54 giregions were significant (59.26\%). Adelaide planes was the reference region with 2012/2013 being the reference year.
%
For Model 3, all years were significant except for 2016/2017 (P=7.532E-01
). 42 out of 50 regions were significant.
% The range of how significant these variable were is important.
%
% How many were important vs how many were not?
%
% was it the same across each of the models? For example was one year/region always bad for every model?
%
\newline
With regard to continuous variables, Model 1 and 2 showed water use, scope 1 emissions and area harvested were significant at 95\% confidence when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope 1 emissions were significant. Model 4 showed scope 1 emissions and water use to only be significant when considered as an interaction with area harvested but not when considered on their own.
\subsubsection{Model Coefficients}
% A map and a table just like the t-test section.
\begin{figure}
\caption{Violine plot of GI Region and Year coefficients for each model.}\label{fig:violin}
\includegraphics{violinplot.pdf}
\end{figure}
